---
title: "Lab 8"
author: "Amy, Mandi, Marielena"
date: "11/15/2021"
output:
  html_document:
    df_print: paged
bibliography: references.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      fig.width = 6.5,
                      fig.height = 8)
library(tidyverse)
library(here)
library(knitr)
```

```{r}
# Load the data

star <- read_csv(here("data", "star.csv"), show_col_types = FALSE)

```

In this lab, we will use the `tidyverse` (@tidyverse) and `here` (@here) packages. We will also use `reader` by @readr and `ggplot2` by @ggplot2, both of which load automatically with the `tidyverse` package.

```{r}
# Code Chunk for Commit 3 
star %>%
  group_by(sex, frl) %>%
  summarize(math_mean = mean(tmathss), math_sd = sd(tmathss), rdg_mean = mean(treadss), rdg_sd = sd(treadss)) %>%
    kable(col.names= c("sex", "frl", "math_mean", "math_sd", "rdg_mean", "rdg_sd"),
        digits = 2,
        booktabs = FALSE)

```

Below is the graph that shows relationship between teacher experience and math scores with regression lines displaying lunch status as free/reduced vs. paid lunch.

```{r}
# Code Chunk for Commit 4

starr <- ggplot(star, aes(totexp, tmathss, color = frl)) +
  geom_point() +
  geom_smooth(method = lm) +
  labs(x = "Teacher Experience (years)",
       y = "Total Math Scale Score",
       title = "Relationship between teacher experience and math scores", subtitle = "Separate regression lines displayed by free/reduced price lunch status") +
  labs(color = "Lunch status") +
  theme(legend.position="bottom")
 
starr +
  scale_color_manual(labels = c("Free/Recuced Price Meals","Paid Meals"),
                     values = c("red", "blue"))
```


\newpage

# References
